Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-15 response_to_reviewers.md

# Response to reviewers

## Reviewer 1

> Patrick O'Leary. Review: "Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics". Authorea. July 26, 2019. DOI: [https://doi.org/10.22541/au.156415458.85375575](https://doi.org/10.22541/au.156415458.85375575)

Portions of the review report quoted here by permissions granted on the original under a CC-BY license.

### Comment 1

* [x] Neither the introduction or the paper highlight the thesis or novel contributions. The reader is left to decide for themselves what aspect they believe are important. This needs to be improved. I found the following list to be reasonable possibilities:

1. Use of cloud computing as an alternative to onsite high-performance computing (HPC).
2. Improvement in public cloud offerings in last 2 to 4 years.
3. A proposed reproducible workflow.
4. The author's experiences.

**Reply**

* The main thesis of the paper is the idea of extending the set of open research objects created and shared for reproducibility (what we call "reproducibility packages"), to the automatic configuration of the computing environment on a cloud service. We explain our contribution in text added at the end of paragraph 3 of the Introduction. We also added a new paragraph at the end of the Introduction to emphasize the point that our paper updates the record with respect to the paper by Freniere and co-authors.
* Because many researchers in "traditional" computational fields (compared to data science) are still highly skeptical of using cloud for their work, we feel it's necessary to provide evidence that it's feasible today to complete CFD studies with cloud computing. Specifically, we need to show that cloud offerings today are practical for parallel computing with GPUs. We added a few sentences to the Abstract and to the last paragraph of the Introduction to emphasize this point.
* Another principal concern of researchers considering cloud resources is the cost. We can't address the issue in this paper in every detail. But we do want to communicate the cost of running the experiments we showcase, and share our ideas about how this concern may be addressed in the future (cost should come down, universities should tackle how to charge indirect costs, and maybe funding agencies could make bulk contracts with providers).

**Changes**

* Improve abstract and introduction to highlight present contributions ([8d998af](https://github.com/barbagroup/cloud-repro/commit/8d998af1c47dbaff37ac713472375bafad45678c)).

---

### Comment 2

* [x] the code snippets breakup the prose with generic, easy to find information such as how to instantiate or run a docker image

**Reply**

* We intend this paper to also serve as a mini-tutorial for researchers wanting to adopt more reproducible practices. (This is mentioned in the beginning of Section 2.) We understand that for this reviewer (an expert in cloud computing, and HPC) these things are obvious. We find among our colleagues and at CFD conferences that containers are still an esoteric technology for most applied computational researchers.

**Changes**

* No changes needed.

---

### Comment 3

* [x] Section One - Defines why reproducibility is essential for science and describes the related work but fails to differentiate their work from past contributions. The reader is left to speculate that it is merely an update to M. Schwab et al., C. Boettiger, C. Freniere et al. works.

**Reply**

* We are citing all of those works in the Introduction. With the new language introduced addressing comment 1, it should be clear now how we extend the work of the previous authors: we propose capturing the cloud environment programmatically and to share with readers the configuration files; we update the record on the observations made by Freniere et al. to the new cloud services introduced in the last two years.

**Changes**

* Improve abstract and introduction to highlight present contributions ([8d998af](https://github.com/barbagroup/cloud-repro/commit/8d998af1c47dbaff37ac713472375bafad45678c)).

---

### Comment 4

Section Two - Walks the reader through the authors' reproducibility workflow outlined in figure 1.

Notes:

* [x] The delete jobs and pool step is missing in figure 1, but presented (including a listing) in the text.
* [x] Do we need to see the content of listing 1 - 4? Why not add a script to the repository and point to it like the YAML config files in examples/snake2d2k35/config_shipyard? 
* [x] The docker build fails on the COPY ../ssh_config stage. Moreover, do the authors want someone to push their image to the authors' docker hub repository? Besides, the repository in footnote 1 contains a typo which highlights the far more significant issues in reproducibility of well-written error-free publications. This paper is a well-written paper, but errors happen.
* [x] The authors generalize that "same container ... can now run at scale." What about the MPI drivers? Does this effect where it can run and what hardware it can use?

**Reply**

* We added the step "Delete jobs and pool" to the workflow in Fig. 1.
* Do we need the listings? — From the reviewer's point of view, these may seem unnecessary, because the reviewer is already an expert in using containers and cloud resources. But we are aiming our paper for readers who are not experts, may have heard of containers as a new and interesting technology, but have never used them. These readers will see from these listings that adopting containers to make their computations more reproducible is not very complicated or time consuming. We want to include these listings as part of the narrative to encourage more researchers to adopt these tools.
* We updated the Dockerfiles to avoid the error message raised during the COPY instruction. We also fixed the typo in the URL of the GitHub repository.
* We do not expect the readers to build the Docker images locally. Indeed, we store the images on DockerHub, so that they can immediately use them. We provide the command-line instructions we used to build the images (as this is part of the workflow). If the readers want to re-build/modify the image locally, we do not expect them to push it to our DockerHub repository. We modified the last paragraph of sub-section 2.1 to reflect our intentions.
* The Docker images were specifically built (on our local workstation) to be able to run MPI applications on RDMA-capable VMs (such as the NC24r instance with a CentOS-based 7.3 HPC image) using multiple-instance tasks on Azure Batch service. The RDMA network on Azure supports MPI traffic for applications running with Intel MPI 5.x (or a later version). (In other words, to take advantage of RDMA on Linux compute nodes, we must use Intel MPI on the nodes.) We added a sentence  over the end of paragraph 4 of the section "Cost Analysis and User Experience" mentioning the Docker images was specifically crafted to be used with Azure Batch service. Thus, we also removed the sentence "same container ... run at scale."

**Changes**

* Fix typo in URL of footnote ([aac96cb](https://github.com/barbagroup/cloud-repro/commit/aac96cba56e532191e700802e250361068553a02)).
* Change directory of the build context so that Docker build does not fail ([67634d9](https://github.com/barbagroup/cloud-repro/commit/67634d915c3a5357dd363b8b8bdc1924e822a3d9)).
* Add step "Delete pool/jobs" to workflow diagram in Fig. 1 ([d612512](https://github.com/barbagroup/cloud-repro/commit/d61251290afc8e59fda135961d70d2804a5adcf8)).
* Remove sentence "same container ... run at scale" ([758e485](https://github.com/barbagroup/cloud-repro/commit/758e485de260cad01c72bdb38f93059593e4fe1b)).
* Mention Docker images were specifically built to run with Azure Batch service ([c908f53](https://github.com/barbagroup/cloud-repro/commit/c908f53bedb699e1ef0853a56ce4353cc21719de)).
* Change "Anyone" to "The reader interested..." ([a84844f](https://github.com/barbagroup/cloud-repro/commit/a84844fca16d25cdfa90d55c35778e2a20130796)).

---

### Comment 5

* [x] At its' core, this paper is describing the use of cloud computing as an alternative to onsite high-performance computing (HPC). At 'scale' is a loaded term in HPC. This paper examines performance improvements in public cloud offerings and compares small runs in the cloud versus a six-year-old onsite HPC system. However, an MPI performance test up to 8 nodes, a mini-application performance tests up to 8 nodes, and a computational fluid dynamics domain science examination of 2 nodes does not adequately explore scaling.

**Reply**

* The language "at scale" indeed can evoke a "leadership computing" scenario (large DOE machines, etc.), and the reviewer is right to protest its use. We rephrased, because we're in the "long tail" setting here, of researchers running in parallel, but moderate size simulations. The runs are still production size for our application, with mesh sizes in the order of 50 million cells, allowing for three-dimensional fluid dynamics studies in the regimes of interest for our research problem.

**Changes**

* Remove sentence "same container ... run at scale" ([758e485](https://github.com/barbagroup/cloud-repro/commit/758e485de260cad01c72bdb38f93059593e4fe1b)).

---

### Comment 6

Section Three - Provides the results in the form of an MPI benchmark and a Poisson mini-application performance analysis, and analysis associated with a standard set of computational science experiments involving flow around a flying snake.

Notes:

* [x] Both the cloud and the six-year old HPC system use FDR Infiniband. Is Azure superior performance a result of tuning, configuration, or age? The analysis provided by this section is that Azure interconnect is improving. Cloud offerings moving from 10 Gbps Ethernet to FDR Infiniband in the past four years makes this result visible without testing. Did we need the OSU benchmarks for verification?
* [x] For the Poisson mini-application, the results again verify Azure has newer hardware than the authors onsite HPC system. However, what was the cause of the variance? Job/Node placement?
* [x] The detailed description of the flying snake workflow is appreciated.

**Reply**

* Is Azure superior performance a result of tuning, configuration, or age? —We didn't apply any manual tuning: both machines are running the same code, but of course the compiler versions are different, and the hardware is different. We are not emphasizing in this paper that performance is "superior" on Azure: just that it is a viable alternative to on-premises HPC clusters (because many researchers continue to be skeptical of cloud). We noticed that the reviewer twice mentions that we're using a "six-year old HPC system." Even if this is an old machine, it is what we have at our university and it is probably the situation for the majority of university researchers that they don't have much choice in regards to the local machines they run on. We certainly are not attempting to do an "apples to oranges" comparison of performance. The point is to dispel the misconception that cloud is (still) inadequate.
* Do we need the OSU benchmark results? We want to showcase that public cloud offerings have improved in the last few years. Our benchmark results show comparable networking performances between our university-managed HPC cluster and Microsoft Azure. We believe it is important to highlight these results as it is still common wisdom that public clouds are inadequate for computational research using HPC. Moreover, Freniere et al. (2016; Computing in Science & Engineering, 18(5), 68) used the same benchmark to compare their local cluster with AWS EC2 and reported performance degradation in networking. With these results, we are updating the readers of CiSE on the improvements of a public cloud such as Microsoft Azure.
* We do not know the cause the variance in runtime for the Poisson benchmark. However, the benchmark was executed 5 times within a single job task (and thus, on the same physical node), so the variation is not due to Job/Node placement. We have updated the caption of Fig. 3 (Poisson benchmark), detailing the number of MPI processes and the number of GPU devices used per node.

**Changes**

* Add information about the number of MPI processes and the number of GPU devices used per node for the Poisson benchmark ([98fccec](https://github.com/barbagroup/cloud-repro/commit/98fccec0a5a0ba7c6d9b4859a20aa81866417f92)).

---

### Comment 7

Section Four - Explores the cost analysis for a typical set of computational science experiments and insights on the user experience.

Notes:

* [x] For the user experience, how much did free computing and augmented support from Microsoft influence the authors' determination to utilize this environment. If it cost 20K, would the authors have completed the project?
* [x] Pricing changes every month, every week, maybe every day. Will any of this analysis be relevant by publication?
* [x] Table 5 will be outdated by the time this article is published. It does not add value.
* [x] How does this cost compare to buying a 2 - 8 node equivalent cluster? 
* [x] Singularity containers appear out of the blue in this section with no description.
* [x] The reference for Table 5 in the text is just (5). Is this a cite, a figure, or a listing.

**Reply**

* We would not have attempted this work, were it not for the sponsored cloud credits. We were indeed curious about reproducibility benefits of cloud computing, and that's why we wrote the proposal to Azure Research. But without the sponsorship, we would not have had research budget for this work. In our opinion, this is one of the reasons to publish this paper: other researchers curious about using cloud need this kind of information before they will jump in. With regards to support, we used the standard channels (support tickets and GitHub issues), and it was not "augmented" support.
* Price will of course change. We feel it needs to go down. The relevancy of publishing the "snapshot" of today's pricing is precisely as back up that prices should drop. However, the cost of the NC24r instance we used in this study has been 3.96 USD per compute hour for the last two years and it's unlikely that it will change by a lot in the next 6 months.
* Table 5 will be outdated, yes, but it is today's situation, under which we operated. It's also the case that the patterns will continue (i.e., the ratio between the different pricing options).
* Cost compared to buying a cluster? We don't really know. We tried to get some helpful data from our IT department, but were denied the information.
* We added a short description about the Singularity container technology at the end of paragraph 3 of the section "Cost Analysis and User Experience."
* We fixed the reference to Table 5 in the manuscript.

**Changes**

* Properly reference Table 5 of the manuscript ([db21f03](https://github.com/barbagroup/cloud-repro/commit/db21f036e8ae47bb4b6ab61d555a28637542ad1a)).
* Add description about Singularity container technology ([df1e0d5](https://github.com/barbagroup/cloud-repro/commit/df1e0d5f009038b2057a3de8a914662972d80769)).

---

## Reviewer 2

> Witherden, Freddie (2019): Review of Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics. figshare. Online resource. DOI: [https://doi.org/10.6084/m9.figshare.9159740.v1](https://doi.org/10.6084/m9.figshare.9159740.v1)

Portions of the review report quoted here by permissions granted on the original under a CC-BY license.

### Comment 1

* [x] Whilst the manuscript is well written the narrative is somewhat muddled. It starts with an overview of reproducible computational research, then pivots to how containers can be employed within the context of cloud computing, then jumping to benchmarks of one particular cloud providers' hardware, and then -- finally -- pivots a final time to a cost analysis of the public cloud for simulations. These are all interesting topics. Indeed, many a conference proceeding has been dedicated to each of these areas. However, by combining them into a single 10 page document this present manuscript fails to do justice to any of these areas. Further, the high degree of specificity will likely have a negative impact the relevance of the manuscript going forwards; a consequence of it being a review of the current state of affairs of a rapidly evolving field. It would therefore be better if it focused on just one or two areas such as "benchmarking cloud computing platforms" or "reproducibility through containers."

**Reply**

* The main goal of this manuscript is to report how to conduct CFD research in a reproducible way on a public cloud, laying out all the tools we used and the steps we undertook. We intend this paper to also serve as a mini-tutorial for researchers wanting to adopt these reproducible practices (we have observed when giving seminars or domain-conference talks that containers haven't disseminated to the CFD community). We use Docker containers to capture the computational environment and Microsoft Azure tools to capture the run-time environment. The degree of specificity is, in part, the point: precisely reproducing our work presumes deploying the same computational environment.
* Right now, researchers using scientific computing are still concerned about cost and performances on public clouds, and this is why we provide benchmark results and are report how much it costs to run our CFD application. Freniere et al. (2016) reported performance degradation on AWS (compared to their local cluster). But in the last three years, cloud providers have improved their offerings for HPC solutions. Thus, another objective is to update the record on the observations made by Freniere et al. (in the same journal) to the new cloud services introduced in the last two years.
* Although cloud computing is a rapidly evolving field, we believe it is important to report on the current state of public cloud offerings for academic applications. 
* The reviewer is a top expert in HPC, and we understand from this point of view it seems the paper does not do justice to the various topics covered. But the intended audience of this paper is not, in fact, either of our reviewers (their expertise was needed, of course, to provide a quality review of the manuscript!). The audience is intended to be researchers using scientific computing (possibly on old and over-subscribed university clusters), who are curious about using cloud resources, and interested in reproducible practices, but need guidelines to adopt these.
* Neither benchmarking cloud computing, nor reproducibility with containers, were a central focus for our paper. We include some benchmark results to update the record with respect to the article by Freniere et al., appearing in the same journal. We use container technology for our reproducible workflow (as others have), but extend the reproducibility ideas to automatic configuration of cloud resources.

**Changes**

* We made several changes, responding to both reviewers, which make the aims of the paper more clear. In particular, the Abstract and Introduction prepare the reader better for the rest of the paper.

---

### Comment 2

* [x] The manuscript only appears to be concerned with reproducibility in the 'now' and pays no consideration to 'link rot' and if one will be able to build and run the proposed containers in 5, 10, or even 20 years. (C.f. Old F77 codes which are expected to remain viable long after the heat death of the universe.) This is one of the most serious issues affecting reproducible research today. 
* [x] Further, the manuscript also glosses over several of the issues regarding deploying containerised applications within an HPC context. One of the most important is with regards to MPI libraries and the fact that many HPC/Cloud environments depend on specific MPI library. For example, Cray machines require Cray MPI, IBM POWER 9 machines require Spectrum MPI, and so on. This results in a 'leaky abstraction' for the container must now concern itself with the idiosyncrasies of the hardware which it is running on.

**Reply**

* Obsolescence of digital research objects, including software libraries and computational environments, is an acknowledged source of non-reproducibility, in the long run. The recent report of the National Academies highlights it so [page?]. Indeed, tools in our workflow that we have no control over (Azure CLI, Batch Shipyard) will likely change, and perhaps not be backwards compatible. That is inevitable. But when they do, our fully documented workflow (via human-readable configuration files) will continue to offer transparency of what we did and how we did it. 
* "issues regarding deploying containerised applications within an HPC context" — Broad portability of our software and workflow is not our objective, and would (arguably) not be justified. Our software is currently only used in research projects within our lab: what reasons would call for the highly skilled and labor intensive software engineering required to deliver broadly portable software and workflow?The goal is, rather, to publish our computational research with deep transparency. The Docker images built for this study were specifically crafted to run on Microsoft Azure with Azure Batch service on RDMA-capable nodes with Linux-based virtual machines. Readers interested in reproducing our analysis should do it under the same conditions, which include the same cloud environment. We have added text in the introduction explaining the limitations of this work with respect to portability issues.

**Changes**

* Added language about limitations regarding portability issues ([97e0512](https://github.com/barbagroup/cloud-repro/commit/97e05126928bea4285c586bfd1f8edc50c0f10ad)).
* Re-arrange last paragraph of the conclusion to emphasize the limitation of the reproducibility, and add citation to the new NASEM report ([6f029e9](https://github.com/barbagroup/cloud-repro/commit/6f029e99103e38b1e4487b08f580a9c1904ba419)).

---

### Comment 3

As highlighted by the authors' in both the manuscript and the Dockerfiles it is necessary (on the Azure platform at least) to use the Intel MPI library. This is highly problematic.

### 2019-08-16 tex/MesnardoBarba2019.tex
Use LaTeX quotes and fix small typos

\IEEEtitleabstractindextext{%
\begin{abstract}
In a new effort to make our research transparent and reproducible by others, we developed a workflow to run and share computational studies on the public cloud Microsoft Azure.
It uses Docker containers to create an image of the application software stack.
We also adopt several tools that facilitate creating and managing virtual machines on compute nodes and submitting jobs to these nodes.
The configuration files for these tools are part of an expanded "reproducibility package" that includes workflow definitions for cloud computing, in addition to input files and instructions.
This facilitates re-creating the cloud environment to re-run the computations under the same conditions.
Although cloud providers have improved their offerings, many researchers using high-performance computing (HPC) are still skeptical about using cloud computing.
Thus, we ran benchmarks for tightly coupled applications to confirm that the latest HPC nodes of Microsoft Azure are indeed a viable alternative to traditional on-site HPC clusters.
We also show that cloud offerings are now adequate to complete computational fluid dynamics studies with in-house research software that uses parallel computing with GPUs.
Finally, we share with the community what we have learned from nearly two years of using Azure cloud to enhance transparancy and reproducibility in our computational simulations.
\end{abstract}
}

@@

Many efforts to develop cyberinfrastructure that supports reproducible research have been launched in past years. 
They address concerns like automatic capture of changes to software (version control systems), persistent data archival, global registration of data identifiers, workflow management, and more. 
But capturing the whole computational environment used in a research project remains one of the most difficult problems. 
Computational researchers often use a multi-layer stack of software applications that can be laborious to build from scratch. 
Container technology like Docker is a recent addition to the reproducibility toolbox \cite{boettiger_2015}. 
In this work, we develop and assess a workflow for reproducible research on the public cloud provider Microsoft Azure, adopting Docker containers and several other tools to automate and fully document scientific computations.
The workflow follows the idea of using container technology to enhance transparency and reproducibility, and to reduce the burden of installing our application software stack.
We go one step further by moving the computational work to Azure cloud resources using tools that programmatically capture the virtual environment configuration.
The configuration files become part of expanded "reproducibility packages" for the study.
This work does not target portability of our software and workflow to diverse high-performance computing (HPC) environments. 
Our goal is, rather, to publish our computational research with deep transparency. 
The workflow we developed and document here is expressly designed for Azure  cloud offerings. 
An interested reader could thus re-run our simulations under exactly the same conditions as we used, provided they are willing and able to create an Azure account.

Universities and national laboratories spend millions of dollars to deploy and maintain on-site HPC clusters.
At the George Washington University, we have access to a cluster called Colonial One.
The cluster is now $6$ years old and approaching its end-of-life.
On average, its computational resources are idle $9\%$ of the time and unavailable to users for roughly 5 days a year (due to maintenance).
Administrators of the cluster have been recently considering integrating cloud-computing platforms in the research-computing portfolio. 
Over the past decade, cloud-computing platforms have rapidly evolved, now offering solutions for scientific applications.
From a user's point of view, a cloud platform offers great flexibility (hardware and virtual machines) with instantaneous availability of infinite (in appearance) computational resources.
No more waiting time in job-submission queues!
This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
On a public-cloud platform---such as Microsoft Azure, Google Cloud, Amazon AWS---with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters. 
Cost models that make sense for researchers, labs, and universities are still unclear. 
Yet, this information is key when making a decision to adopt a cloud workflow for research.

@@

Our research lab is interested in understanding the aerodynamics of flying animals via CFD simulations.
One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea Paradisi}, that lives in South-East Asia.
This arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
The so-called ``flying snake'' jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).

@@

We submitted a job on Azure Batch (with Batch Shipyard,) to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
The cross-section has a chord-length $c=1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
The Reynolds number, based on the freestream speed, the body chord-length, the kinematic viscosity, is set to $Re=2000$.
The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just over $2.9$ million cells.
The grid is uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
The discretization of the immersed boundary has the same resolution as the background fluid grid.
A convective condition was used at the outlet boundary while freestream conditions were enforced on the three other boundaries.
The job was submitted to a pool of two \texttt{NC24r} nodes, using $12$ MPI processes and $2$ GPU devices per node.
It completed $200,000$ time steps (i.e., $80$ time units of flow simulation with time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours (wall-clock time).

@@

Fig. \ref{fig:force_coefficients} compares the history of the force coefficients between the two- and three-dimensional configurations.
The force coefficients resulting from the two-dimensional simulation of the snake are higher than those obtained for the snake cylinder; we computed a relative difference of $+37.9\%$ and $+14.4\%$ for the time-averaged drag and lift coefficient, respectively (see Table \ref{tab:force_coefficients}).
Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.
The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for direct numerical simulation at Reynolds number $2,000$, but acceptable for our exploratory analysis.
A finer grid would be preferable to capture the flow dynamics in detail, but the purpose of this paper is not targeting the physics.
We did however run a simulation on a finer grid (about $233$ million cells) resulting in a relative difference (with respect to the "coarse"-grid simulation) of $+6.5\%$ and $+3\%$ for the time-averaged drag and lift coefficients, respectively.
We decided to continue this work with the coarser grid due to the large cost difference (see Section \ref{sec:cost}).
Details about this fine-grid simulation are available as supplementary material on the GitHub repository for this study.\footnote{\url{https://nbviewer.jupyter.org/github/barbagroup/cloud-repro/blob/master/misc/independence/grid.ipynb}}

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship (in terms of cloud credits) to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run CFD simulations, including a couple dozens of snake simulations.
(The output of those simulations is now being processed to further analyze the complex flow dynamics generated behind the snake model.)
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)
The three-dimensional simulation on the finer grid ($233$ million cells) ran on $6$ \texttt{NC24r} instances and cost about $7965$ USD to compute $100,000$ time steps (cost not included in \ref{tab:azure_charges}).
This is more than $7$ times the cost we paid for the "coarse"-grid run!
It would have been too expensive to run a batch of simulations on the finer grid for our exploratory analysis of the flow around the snake cylinder.

>>>>

\IEEEtitleabstractindextext{%
\begin{abstract}
In a new effort to make our research transparent and reproducible by others, we developed a workflow to run and share computational studies on the public cloud Microsoft Azure.
It uses Docker containers to create an image of the application software stack.
We also adopt several tools that facilitate creating and managing virtual machines on compute nodes and submitting jobs to these nodes.
The configuration files for these tools are part of an expanded ``reproducibility package'' that includes workflow definitions for cloud computing, in addition to input files and instructions.
This facilitates re-creating the cloud environment to re-run the computations under the same conditions.
Although cloud providers have improved their offerings, many researchers using high-performance computing (HPC) are still skeptical about using cloud computing.
Thus, we ran benchmarks for tightly coupled applications to confirm that the latest HPC nodes of Microsoft Azure are indeed a viable alternative to traditional on-site HPC clusters.
We also show that cloud offerings are now adequate to complete computational fluid dynamics studies with in-house research software that uses parallel computing with GPUs.
Finally, we share with the community what we have learned from nearly two years of using Azure cloud to enhance transparancy and reproducibility in our computational simulations.
\end{abstract}
}

@@

Many efforts to develop cyberinfrastructure that supports reproducible research have been launched in past years. 
They address concerns like automatic capture of changes to software (version control systems), persistent data archival, global registration of data identifiers, workflow management, and more. 
But capturing the whole computational environment used in a research project remains one of the most difficult problems. 
Computational researchers often use a multi-layer stack of software applications that can be laborious to build from scratch. 
Container technology like Docker is a recent addition to the reproducibility toolbox \cite{boettiger_2015}. 
In this work, we develop and assess a workflow for reproducible research on the public cloud provider Microsoft Azure, adopting Docker containers and several other tools to automate and fully document scientific computations.
The workflow follows the idea of using container technology to enhance transparency and reproducibility, and to reduce the burden of installing our application software stack.
We go one step further by moving the computational work to Azure cloud resources using tools that programmatically capture the virtual environment configuration.
The configuration files become part of expanded ``reproducibility packages'' for the study.
This work does not target portability of our software and workflow to diverse high-performance computing (HPC) environments. 
Our goal is, rather, to publish our computational research with deep transparency. 
The workflow we developed and document here is expressly designed for Azure  cloud offerings. 
An interested reader could thus re-run our simulations under exactly the same conditions as we used, provided they are willing and able to create an Azure account.

Universities and national laboratories spend millions of dollars to deploy and maintain on-site HPC clusters.
At the George Washington University, we have access to a cluster called Colonial One.
The cluster is now $6$ years old and approaching its end-of-life.
On average, its computational resources are idle $9\%$ of the time and unavailable to users for roughly 5 days a year (due to maintenance).
Administrators of the cluster have been recently considering integrating cloud-computing platforms in the research-computing portfolio. 
Over the past decade, cloud-computing platforms have rapidly evolved, now offering solutions for scientific applications.
From a user's point of view, a cloud platform offers great flexibility (hardware and virtual machines) with instantaneous availability of infinite (in appearance) computational resources.
No more waiting time in job-submission queues!
This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
On a public-cloud platform---such as Microsoft Azure, Google Cloud, Amazon AWS---with a ``pay-as-you-go'' type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters. 
Cost models that make sense for researchers, labs, and universities are still unclear. 
Yet, this information is key when making a decision to adopt a cloud workflow for research.

@@

Our research lab is interested in understanding the aerodynamics of flying animals via CFD simulations.
One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea paradisi}, that lives in South-East Asia.
This arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
The so-called ``flying snake'' jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).

@@

We submitted a job on Azure Batch (with Batch Shipyard) to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
The cross-section has a chord-length $c=1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
The Reynolds number, based on the freestream speed, the body chord-length, the kinematic viscosity, is set to $Re=2000$.
The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just over $2.9$ million cells.
The grid is uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
The discretization of the immersed boundary has the same resolution as the background fluid grid.
A convective condition was used at the outlet boundary while freestream conditions were enforced on the three other boundaries.
The job was submitted to a pool of two \texttt{NC24r} nodes, using $12$ MPI processes and $2$ GPU devices per node.
It completed $200,000$ time steps (i.e., $80$ time units of flow simulation with time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours (wall-clock time).

@@

Fig. \ref{fig:force_coefficients} compares the history of the force coefficients between the two- and three-dimensional configurations.
The force coefficients resulting from the two-dimensional simulation of the snake are higher than those obtained for the snake cylinder; we computed a relative difference of $+37.9\%$ and $+14.4\%$ for the time-averaged drag and lift coefficient, respectively (see Table \ref{tab:force_coefficients}).
Two-dimensional computational simulations of fundamentally three-dimensional flows lead to incorrect estimation of the force coefficients, as is well known\cite{mittal_balachandar_1995}.
The grid used for the three-dimensional simulation contains about $46$ million cells and is somewhat coarse for direct numerical simulation at Reynolds number $2,000$, but acceptable for our exploratory analysis.
A finer grid would be preferable to capture the flow dynamics in detail, but the purpose of this paper is not targeting the physics.
We did however run a simulation on a finer grid (about $233$ million cells) resulting in a relative difference (with respect to the ``coarse''-grid simulation) of $+6.5\%$ and $+3\%$ for the time-averaged drag and lift coefficients, respectively.
We decided to continue this work with the coarser grid due to the large cost difference (see Section \ref{sec:cost}).
Details about this fine-grid simulation are available as supplementary material on the GitHub repository for this study.\footnote{\url{https://nbviewer.jupyter.org/github/barbagroup/cloud-repro/blob/master/misc/independence/grid.ipynb}}

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship (in terms of cloud credits) to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run CFD simulations, including a couple dozens of snake simulations.
(The output of those simulations is now being processed to further analyze the complex flow dynamics generated behind the snake model.)
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)
The three-dimensional simulation on the finer grid ($233$ million cells) ran on $6$ \texttt{NC24r} instances and cost about $7965$ USD to compute $100,000$ time steps (cost not included in \ref{tab:azure_charges}).
This is more than $7$ times the cost we paid for the ``coarse''-grid run!
It would have been too expensive to run a batch of simulations on the finer grid for our exploratory analysis of the flow around the snake cylinder.
